---
title       : Linear Regression Model Explorer
subtitle    : Easily explore data and regression model features  
author      : demgenman@outlook.com
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## OLD - Data summary 

Data counts:
- Nr of observations (rows)
- Nr of variables (columns)
- Total nr of NA values in the data set

Summary statistics:
- Output of "summary()" function: min, max, median, mean, quantiles, NA counts

Basic plots:
- Histogram (of response variable)
- Box plot (of response and selected predictors)

--- .class #id 

## OLD - Sample data summary 

```{r echo=FALSE}
data(attitude)
```
Nr of observations: `r dim(attitude)[1]`, 
Nr of variables: `r dim(attitude)[2]`,
Total NA values: `r sum(is.na(attitude))`.

```{r echo=FALSE, results='asis'}
library(xtable)
print(xtable(summary(attitude[,c("rating", "complaints", "learning")])), type="html")
```

```{r echo=FALSE, fig.height=3.5, fig.width=4.5}
hist(attitude$rating, main="Histogram of rating", xlab="rating")
boxplot(attitude[,c("rating", "complaints", "learning")], plot=TRUE)

```
--- .class #id 

## OLD - Modeling

Formula: Response ~ Predictor(s) + Interaction(s) + Intercept

Create model:
- Select response (dependent) variable, predictor (independent) variables, any interactions.
- Indicate if regression is to be performed with or without intercept.

LRME automatically populates choices based on your selections.
- Lists all variables found in the selected data set
- Hides the selected response variable from the predictor choices
- Generates choices for possible predictor interactions

Notes:
- All variable choices are reset when you select a different data set.
- The default response variable is the first variable found in the data set.

--- .class #id 

## OLD - Regression model summary statistics

```{r, echo=FALSE, results='asis'}
data(attitude)
fit.lm <- lm("rating ~ complaints + privileges", data = attitude)
f <- as.character(formula(fit.lm))
```

Model summary
- Formula: `r paste("Formula: ", f[2], f[1], f[3])`

```{r, echo=FALSE, results='asis'}
print(xtable(summary(fit.lm)), type="html")
```

Confidence interval
```{r, echo=FALSE, results='asis'}
print(xtable(confint(fit.lm)), type="html")
```

Model statistics: RSE, R squared, F-statistic, DF

--- .class #id 

## OLD - Assumptions and limitations

Data sets:
- "Well formatted": no transcoding or format changes needed
- Header row present, variables that are numeric or can be converted to numeric 

Data set plots:
- Boxplot: non-numeric variables will be coerced to numeric in the plot

Linear regression model:
- Numeric response
- Numeric and categorical predictors
- No transformations
- No higher order (polynomial) predictors



