---
title       : Linear Regression Model Explorer
subtitle    : Easily explore data and regression model features  
author      : demgenman at outlook com
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Linear Regression Model Explorer

Use LRM Explorer (LRME) to quickly explore a data set, apply a linear regression model and obtain various summary statistics.

Features:
- Load and/or select data set
- View data summary
- Create linear regression model
- View model diagnostics 

Model formula: Response ~ Predictor(s) + Interaction(s) + Intercept

--- .class #id 

## Data analysis

Built-in data sets (no upload needed):
- attitude
- ChickWeight
- mtcars

Data set provided by user:
- Upload "well-formatted" csv file
- After uploading select data set "uploaded data"

Statistics:
- Data counts: row, cols, NA values
- Variable summaries: min, max, median, mean, quantiles, NA
- Plots: Histogram, box plot

--- .class #id 

## Modeling

Formula: Response ~ Predictor(s) + Interaction(s) + Intercept

Create linear regression model:
- Select dependent variable (response), independent variables (predictors) and any interactions.
- Indicate if regression is to be performed with or without intercept.

Model parameters, statistics and diagnostics:
- Coefficients and confidence intervals
- RSE, R squared, F-statistic, DF
- Plots: pairs, diagnostic plot grid, residuals to fitted, hat values

--- .class #id 

## Sample plots

```{r, echo=FALSE}
        # Here we use some third party code to extend the functionality of the pairs plot
        # panel extensions for pairs function
        # source: R Documentation, pairs {graphics}
        panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
        {
            usr <- par("usr"); on.exit(par(usr))
            par(usr = c(0, 1, 0, 1))
            r <- abs(cor(x, y))
            txt <- format(c(r, 0.123456789), digits = digits)[1]
            txt <- paste0(prefix, txt)
            if(missing(cex.cor)) cex.cor <- 0.6/strwidth(txt)
            text(0.5, 0.5, txt, cex = cex.cor * r)
        }
        panel.hist <- function(x, ...)
        {
            usr <- par("usr"); on.exit(par(usr))
            par(usr = c(usr[1:2], 0, 1.5) )
            h <- hist(x, plot = FALSE)
            breaks <- h$breaks; nB <- length(breaks)
            y <- h$counts; y <- y/max(y)
            rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
        }
        # source: http://stackoverflow.com/questions/15271103/how-to-modify-this-correlation-matrix-plot
        # Didzis Elferts
        panel.smooth<-function (x, y, col = "blue", bg = NA, pch = 18, 
                                cex = 0.8, col.smooth = "red", span = 2/3, iter = 3, ...) 
        {
            points(x, y, pch = pch, col = col, bg = bg, cex = cex)
            ok <- is.finite(x) & is.finite(y)
            if (any(ok)) 
                lines(stats::lowess(x[ok], y[ok], f = span, iter = iter), 
                      col = col.smooth, ...)
        }
        # End of third party code
```


```{r, echo=FALSE, results='asis'}
data(attitude)
fit.lm <- lm("rating ~ complaints + privileges", data = attitude)
f <- as.character(formula(fit.lm))
```

Formula: `r paste(f[2], f[1], f[3])` (in attitude data set)

```{r, echo=FALSE, fig.height=3.5, fig.width=4}
modelVars <- c("rating", "complaints", "privileges")
pairs(attitude[, modelVars], main = "Pairs plot", lower.panel=panel.smooth, upper.panel=panel.cor, diag.panel=panel.hist)
oldpar <- par(mfrow=c(1,2)); plot(fit.lm, which=c(1:3,5), cex=1.2); par(oldpar)
plot(predict(fit.lm), residuals(fit.lm), xlab="Fitted values", ylab="Residuals", main="Residuals")
plot(hatvalues(fit.lm), ylab = "Hat values", main="Hat values", xlab="Observation nr", cex=1.2)
```

--- .class #id 

## Assumptions and limitations

Data sets:
- "Well formatted": no transcoding or format changes needed
- Header row present, variables that are numeric or can be converted to numeric 

Data set plots:
- Boxplot: non-numeric variables will be coerced to numeric in the plot

Linear regression model:
- Numeric response
- Numeric and categorical predictors
- No transformations
- No higher order (polynomial) predictors

